Supporting information

### 2019-08-23 EAshiklomanovSA2.Rmd
Add bootstrap to SA2

```{r create_traits}
set.seed(12345) # For reproducibility
library(mvtraits)

true_mu <- c(0, 0)
true_cov <- matrix(c(1, 0.8, 0.8, 1), nrow = 2)
Y_all <- random_mvnorm(1000, true_mu, true_cov)
colnames(Y_all) <- c("A", "B")
plot(Y_all, pch = 19)
```

@@

```{r remove_na}
Y <- Y_all
Y[sample.int(2000, 1000)] <- NA
plot(Y_all, pch = 19, col = "grey")
points(Y, pch = 19, col = "black")
legend(
  "topleft",
  legend = c("True missing", "Present"),
  col = c("grey", "black"),
  pch = 19,
  bg = "white"
)
```

@@

>>>>

```{r create_traits}
set.seed(12345) # For reproducibility
library(mvtraits)
true_mu <- c(0, 0)
true_cov <- matrix(c(1, 0.8, 0.8, 1), nrow = 2)
Y_all <- random_mvnorm(1000, true_mu, true_cov)
colnames(Y_all) <- c("A", "B")
plot(Y_all, pch = 19)
```

@@

```{r remove_na}
Y <- Y_all
ymiss <- sample.int(2000, 1000)
# Save true values for validation
ymiss_true <- Y[ymiss]
Y[ymiss] <- NA
plot(Y_all, pch = 19, col = "grey")
points(Y, pch = 19, col = "black")
legend(
  "topleft",
  legend = c("True missing", "Present"),
  col = c("grey", "black"),
  pch = 19,
  bg = "white"
)
```

@@

The `mvtraits` package provides the convenience function `fit_mvnorm` for performing this entire procedure automatically.

```{r}
results <- fit_mvnorm(Y)
results$stats$mu$Mean
true_mu
results$stats$Sigma$Mean
true_cov
```

It also provides a function for bootstrapping the results of a model fit this way:

```{r}
data_boot <- bootstrap_missing(results, Y)
boot_means <- apply(data_boot, c(1, 2), mean)[ymiss]
plot(ymiss_true ~ boot_means, pch = 19,
     xlab = "Imputed values (bootstrapped mean)",
     ylab = "True missing values")
abline(0, 1, lty = "dashed")
```

We can see that for all data points where at least one observation was available as constraint, the algorithm imputed values that were close to the true values.
However, where values for both traits were missing, the algorithm falls back to the global mean, which has the same statistical properties as the missing data (i.e. central tendency and spread) but doesn't match the true values.
